---
title: "Kong-Chapter7"
author: "Vivian Kong"
date: "11/12/2016"
output: html_document
---

## 7.24 Nutritions at Starbucks
(a). Calories and amount of carbohydrates is positive linear relationship.
(b). explanatory variable is amount of carbohydrates and the response variable is the calories.
(c). We want to predict the calories of the starbucks by looking at the amount of carbohydrates.
(d). It satisfies the linearility, nearly normal residual, constant variability and independent obervations.

## 7.26 Body Measurements
(a).
```{r}
b1 <- (9.41 / 10.37) * 0.67
b0 <- (b1 * (0-107.2))+ 171.14
```
\[\hat{y}= `r b0` + `r b1`x\]

(b). The intercept is te height at girth equal to 0cm. The slope is when shoulder increase by 1 cm the height will increase by 0.6 cm.
(c).

```{r}
r2 <- 0.67^2
```
The \(R^2 =`r r2`\). 45% of the variance of the height depends on the variance of the shoulder.
(d). 
```{r}
height_shoulder <- function(girth)
{
  height <- b0 + b1 * girth
  return(height)
}
predict <- height_shoulder(100)
predict
```

(e). Residual is -6

(f). no, it is not appropriate because it is almost 5 standard deviation below the mean shoulder girth.

## 7.30 Cats
(a).
\[\hat{y} = -0.357 + 4.034x\]

(b). When the cat's body height is 0, the heart weight will be negative. 

(c). The slope is 4.034. when the cat's body weight increases by 1 gram, the heart weight will increase by 4.034 grams.

(d). The \(R^2\) is 64.66%. 64.66% of the variation the heart weight depends on the variabtion of the cat's body.

(e). 
```{r}
r <- sqrt(0.6466)
r
```

## 7.40 Rate my Professor

(a). 
```{r}
b1 <- (3.9983 - 4.010) / -0.0883
b1
```
(b).
It provides very strong positive relationship between teaching evaluation and beauty, since P-value is so much less than the significant level.

(c). Linearility : it is a little bit weak trend but it is satisfied
Nearly normal residual: In the QQ plot, they are approximately normal.
Constant Variability : The scatterplot of the residuals appears to have constant variability.
Independent Observations: 463 professors shoulde be the single obervation.

