---
title: "Chapter 8 HW"
author: "Vivian Kong"
date: "11/21/2016"
output: html_document
---

## 8.2 Baby Weights, Part II
#### a)
\[y=120.07 - 1.93 x_{parity}\]

#### b)
slope is -1.93 which meas 1 parity increasing will decrease the baby's weigh by 1.93 oz. The first baby is 118.14 oz. 

#### c) 
since p-value is 0.1052 which is not a significant relationship between the average birth weigh and parity.

## 8.4 Absenteeism

#### a)
\[y = 18.93 - 9.11 x_{eth} + 3.10 x_{sex} + 2.15 x_{lrn}\]

#### b)
The slope of eth means that all else being the same, when eth increase by 1, it will decrease the y by 9.11 days.
The slope of sex means that all else being the same, when the subject is male, y will increase by 3.10 days.
The slope of lrn means that all else being the same, when the subject is a slow learner, y will increase by 2.15 days.

#### c)
```{r}
eth <- 0
sex <- 1
lrn <- 1
actualDayMissed <- 2

absDaysPred <- 18.93 - 9.11 * eth + 3.1 * sex + 2.15 * lrn
absDaysPred

residual <- actualDayMissed - absDaysPred
residual
```

The residual is `r residual` days.

#### d)
```{r}
n <- 146
k <- 3
varRes <- 240.57
varOut <- 264.17

r2 <- 1- (varRes/ varOut)
r2
adjustedr2 <- 1- (1 - r2) * ((n-1) / (n-k-1))
adjustedr2
```

##8.8 Absenteeism

In this case, we will remove the ethnicity first.

##8.16 Challenger disaster

#### a) 
When the temperature is less than 66, there is more damaged O-rings. 

#### b)
The key components are the Intercept and the Temperature values. Z-value and P-value help us distinguish the significant levels.

#### c) 
\[\log_e(\frac{p_i}{1-p_i}) = 11.6630 - 0.2162 x_{temp}\]

#### d)
Since the p-value is very close to 0, it indicates that the O-ring failure is strongly correlated to temperature. 

## 8.18 Challenger disaster, Part II

#### a)
```{r}
temp <- 51
p <- exp(11.6630-(0.2162 * temp)) / (1+exp(11.6630- (0.2162 * temp)))
p

temp1<- 53
p2 <- exp(11.6630-(0.2162 * temp1)) / (1+exp(11.6630- (0.2162 * temp1)))
p2

temp2 <- 55
p3 <-exp(11.6630-(0.2162 * temp2)) / (1+exp(11.6630- (0.2162 * temp2)))
p3
```

####b)
```{r}
library(ggplot2)
temps <- seq(51, 71, by=2)
probs <- c(p, p2, p3, 0.341, 0.251, 0.179, 0.124, 0.084, 0.056, 0.037, 0.024)
df_prob <- data.frame(Temperature = temps, Prob_Damage = probs)
g1 <- ggplot(df_prob) + geom_line(aes(x=df_prob$Temperature, y=df_prob$Prob_Damage))
g1
```

####c)
We need more sufficient data. For the logistic model: x is linearly related to \[logic((p_i))\]. it looks like that they seem to have a linear relationship to the probability of damage. y is independent of the other outcomes.