---
title: "Chapter 6"
author: "Vivian Kong"
date: "10/29/2016"
output: html_document
---

## 6.6 2010 Healthcare Law.

a. False. The confiden interval appies to the population.
b. True.
c. True.
d. False. 90% will have a lower margin of error. 

## 6.12 Legalization of marijuana

a. It is a sample statistics because 1259 US residents are sample of American population.
b. 
```{r}
SE <- sqrt((0.48 * (1-0.48))/1259)
LI <- 0.48 - (qnorm(0.975)*SE)
HI <- 0.48 +(qnorm(0.975)*SE)
LI
HI
```

c. 1. Observations are independent. The sample is nore more than 10% of population. 
   2. Success-failure condition. The success and failure are both greater than 10. 

d. I think the news' conclusion is biased because the sample take from U.S can not represent the entire population.

## 6.20 Legalize Marijuana, Part II
```{r}
n <- (0.48 * (1-0.48))/ (0.02 / (qnorm(0.975)))^2
ceiling(n)
```

## 6.28 Sleep deprivation
```{r}
SE_cal <- sqrt((0.08 * (1-0.08))/11545)
SE_org <- sqrt ((0.088 * (1-0.088))/4691)
SE_org_cal <- sqrt(SE_cal+SE_org)
LI <- (0.088-0.08) - (qnorm(0.975)*SE_org_cal)
UI <- (0.088-0.08)+ (qnorm(0.975)*SE_org_cal)
LI
UI
```
Since the interval is between -15% to -17%. This means that the proportion of Oregonians who are sleep deprived can be as much as 15% to 17% less than Californians. 

## 6.44 Barking deer

a. H0: The barking deer does not prefer a certain habitat to forage.
   HA: The barking deer has certain habitats that it prefer to forage.

b. A chi-square test.

c. 1. Independence. Each habitat are independent.
   2. Sample size. 

d.
```{r}
   Zwood <- (0.9-4.8)^2/4.8
   Zgrass <- (3.8 - 14.7)^2 / 14.7
   Zforest <- (14.3-39.6)^2 / 39.6
   Zoth <- (81.0-40.9)^2 / 40.9
   Z_all <- Zwood + Zgrass + Zforest + Zoth
   Z_all
   1-pchisq(Z_all, 3)
```

Since P-value is very very small, we can reject H0, accept HA.

## 6.48 Coffee and Depression.
a. Chi-Square test
b. 
H0: There is no relationship between coffee consumption and clinical depression
HA: There is relationship between coffee consumption and clinical depression

c. 
```{r}
p_depressed <- (2607/50739) * 100
p_normal <- ( 48132/50739) * 100
exp_cnt <- 6617 * 0.0514
obs_cnt <- 373
(obs_cnt - exp_cnt)^2 / exp_cnt
```

d. 
```{r}
df <- (5-1) * (2-1)
df
1- pchisq(20.93, df)
```

f. Since P-value is very small, we will reject H0, accept HA.

g. Yes. I agree with it because the result shows that there is a relationship between the coffee consumption and the depression.

