---
title: "Kong-HW5"
author: "Vivian Kong"
date: "October 11, 2016"
output: html_document
---


## 5.6 Working backwards, PartII. 

```{r}
# Look up the t value for 90% CI

CI <- 0.90
alpha <- 1-CI
t_area <- (1-(alpha/2))

# degree of freedom
n <- 25
degree_freedom <- n - 1

# t value
t <- qt(t_area, degree_freedom)
a <- rbind(c(1, t/5),
           c(1, (-t)/5))
b <- c(77,65)
solve(a, b)

# margin of error
margin_of_error <- (77-65)/2
margin_of_error
```
\
**The values are:**\
Sample mean is 71. Sample standard deviation is 17.5. Margin of error is 6.

## 5.14 SAT scores
(a).

```{r}
margin_of_error1 <- 25
s.d <- 250
z <- qnorm(0.95)
z
n <- ((z * s.d)/ margin_of_error1)^2
n
```

(b). Luke's sample size should be larger than Raina's.

(c). 

```{r}
margin_of_error1 <- 25
s.d <- 250
z <- qnorm(0.99)
z
n <- ((z * s.d)/ margin_of_error1)^2
n
```

## 5.20 High School and Beyond, Part I. 

(a). The difference in schores is approximately normal. Most people's reading and writing scores are clustered to 0.

(b). It is independent for each other.

(c). H0: There is no difference in the average of reading and writing score.
     Ha: There is difference in the average of reading and writing score.
     
(d). They are independent and the observation is aprroximately normal distribution.

(e). 
```{r}
mean_diff <- -0.545
s.d <- 8.887
n <- 200

# Find the standard erro

s.d.e <- s.d / sqrt(n)

# T stat
t <- (mean_diff - 0)/ s.d.e
degree_freedom1 <- n - 1
p <- pt(t, df=degree_freedom1)
p
```

P is more than 0.05 we fail to reject the null hypothesis. 

(f). It is Type II error.

(g). Since we fail to reject null hypothesis, there is no difference between writing and reading.

## 5.32 Fuel efficiency of manual and automatic cars, Part I.

H0: There is no difference between automatic car's MPG and manual car's MPG.
Ha: There is differnce between automatic car's MPG and manual car's MPG.

```{r}
n <- 26
mean_diff1 <- 16.12 - 19.85
standard_erro_diff <- sqrt((3.58^2/n)+(4.51^2/n))
standard_erro_diff

t1 <- (mean_diff1 - 0)/ standard_erro_diff
t1 
P_value <- pt(t1, df=n-1)
P_value
```

# Since the p-value is less than 0.05, we reject the Null Hypothesis and accept alternative hypothesis. In this case, there is strong evidence to support the difference between manual and automatic transmissions.

## 5.48 Work hours and education. 
(a). H0:There is no difference in average hours worked across the 5 groups.
     Ha: At least 1 group has a difference in the average hours worked with the other groups.

(b). The observations are independent and approximately normal, and the variablity across the groups is about the same.

(c). 
```{r}
n <- 1172
k <- 5
df1 <- k -1
df2 <- n-k
mean_total <- 40.45
group <- data.frame(n=c(121,546,97,253,155),
                    sd=c(15.81,14.97,18.1,13.62,15.51),
                    mean=c(38.67, 39.6, 41.39,42.55,40.85))
sg <- sum (group$n * (group$mean - mean_total)^2)
sg

Msg <- (1/df1)*sg
sse <- 267382
mse <- sse / df2
mse

F <- Msg / mse
F
```
|         |Df   | Sum Sq  |Mean Sq| F value  | Pr (>F) |
|---------|-----|---------|-------|----------|---------|
|degree   | **4**    |  **2004.1** | 501.54  | **2.186745** | 0.0682 |
|Residuals| **1167** |  267382| **229.12**   |              |
|Total    | **1171** | **269386.1** |        |              |

(d). Since P-value = 0.0682, that is greater than 0.05, we fail to reject the null hypothesis. There is no difference between groups.