---
title: "Chapter 3"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 3.2 Area under the curve
What percent of a standard normal distribution N (mena is 0, s.d is 1) is found in each region?
(a). Z > -1.13
```{r}
normalPlot(mean=0, sd=1, bounds= c(-1.13,4), tails=FALSE)
```
p(z > -1.13)= 87.1%

(b). Z < 0.18
```{r}
normalPlot(mean=0, sd=1, bounds = c(-4,0.18),tails = FALSE)
```
P(z < 0.18)= 57.1%

(c). Z >8
```{r}
normalPlot(mean=0, sd=1, bounds=c(8, 100), tails = FALSE)
```
P(Z>8)=0

(d). |z| < 0.5
```{r}
normalPlot(mean=0, sd=1, bounds=c(-0.5, 0.5), tails = FALSE)
```
P(-0.5<z<0.5)= 38.3%

## 3.4 Triathlon times
Mean of men : 4313 seconds, s.d of men: 583 seconds
Mean of women : 5261 seconds, s.d of women: 807 seconds.
(a).  Men 30-34 group: Mean(mu)= 4313 seconds, standard deviation = 583
      Women 25-29 group: Mean(mu)= 5261 seconds, standard deviation = 807

(b)What are the Z-scores for Leo's and Mary's finishing times? What do these Z-scores tell you?
```{r}
Z1 <- (4948-4313)/583
Z1
Z2 <- (5513-5261)/807
Z2
```
Z(leo)=1.089
Z(Mary)=0.312
Both of their z scores are greater than 0 that means their time is longer than the average. Their scores not that good.
(c). Did Leo or Mary rank better in their respective groups?
Mary ranks better in their respective groups because Mary has smaller z score and it means that she took shorter period of time in the respective group.
(d). What percent of the triathletes did Leo finish faster than in his group?
```{r}
normalPlot(mean=0, sd=1, bounds = c(1.089,4),tails = FALSE)
```
P(x>1.089)=13.8%
(e). What percent of the triathletes did Mary finish faster than in her group?
```{r}
normalPlot(mean=0, sd=1, bounds = c(0.312,4), tails = FALSE)
```
P(x>0.312)=37.7%
(f). If the distributions of finishing times are not nearly normal, would you answers to parts (b)-(e) change?Explain your reasoning.
For a large amount of data, normally n > 30, Central Limit Theorem applies, then answers to parts (b)-(e) would not change. However, if the amount of athelets is less than 30, then the answer of (b)-(e) will change.

## 3.18 Heights of female college students.
(a). The mean height is 61.52 inches with a s.d of 4.58 inches. Use this information to determine if the heights approximately follow the Rule.
Approximately 68% will fall within 56.94 inches to 66.1 inches. By observing the data, we have 17 data values fall within this range. 17/25 = 0.68. 
Approximately 95% will fall within 52.36 inches to 70.68 inches. By observing the data, we have 24/25=0.96.

(b). Do these data appear to follow a normal distribution? Explain your reasoning using the graphs provided below.
```{r}
x <- c(57,66,69,71,72,73,74,77,78,78,79,79,81,81,82,83,83,88,89,94)
qqnorm(x)
qqline(x)
```
The data set that is nearly normal where the points closely follow the line. It will follow the rule. 

## 3.22 Defective rate
A machine that produces a special type of transistor (a component of computers) has a 2% defective rate. The production is considered a random process where each transistor is independent of the others.
(a). What is the probability that the 10th transistor produced is the first with a defect.
P(the 10th transistor)= (0.98)^9 * (0.02)= 0.01667 =1.67%

(b). What is the probability that the machine produces no defective transistors in a batch of 100?
P(100)=(0.98)^100=0.1323

(c). On average, how many transistors would you expect to be produced before the first with a defect? What is the standard deviation?
 E(x)=1/p = 1/ 0.02 =50
 s.d(x)= (1-p)/p^2 = sqrt((1-0.02)/(0.02)^2)=49.50
 
 (d). Another machine that also produces transistors has a 5% defective rate where each transistor is produced independent of the others. On average how many transisors would you expect to be produce with this machine before the first with a defect? What is the standard deviation?
 E(x)= 1/p = 1 / 0.05 =20
 sd(x)= sqrt ( (1-0.05)/0.05^2)=19.49
 
 (e). Based on your answer to parts (c) and (d), how does increasing the probability of an event affect the mean and standard deviation of the wait time until success?
 when the probability is increasing, the mean and standard deviation is decreasing.
 
 ## 3.38 While it is ofen assumed that the probabilities of having a boy or a girl are the same. the actual probability of having a boy is slightly higher at 0.51. Suppose a couple plans to have 3 kids.
 (a). Use the binomial model to calculate the probability that two of them will be boys.
 P(x=2 boys)= 3C2 (.51)^2*(0.49)=0.3823
 
 (b). Write out all possible orderings of 3 children, 2 of whom are boys.
 List: BBG,BGB,GBB
 P(BBG)=(0.51)(0.51)(0.49)=0.1274
 P(BGB)=0.1274
 P(GBB)= 0.1274
 P(2 boys)=p(BBG)+p(BGB)+p(GBB)=0.3823
 
 (c). If we wanted to calculate the probability that a couple who plans to have 8 kids will have 3 boys, briefly describe why the approach from part (b) would be more tedious than the approach from part (a)
 
 Since there are 8C3= 56 ways to make the whole list, to list each one, it will take a lot of time
 
 ## 3.42 Serving in Volleyball.
 A not-so-skilled volleyball player has a 15% chance of making the serve, which involves hitting the ball so it passes over the net on a trajectory such that it will land in the opposing team's court. Suppose that her seves are independent of each other.
 
(a). What is the probability that on the 10th try she will make her 3rd successful serve?
P(x)= 9C2 (0.85)^7(0.15)^3= 0.0390

(b). Suppose she has made two successful serves in nine attempts. What is the probability that her 10th serve will be successful?
P(x)= 0.15 because her serves are independent of each other.

(c). Even though parts (a) and (b) discuss the same scenario, the probabilities you calculated should be different. Can you explain the reson for theis discrepancy?
because the player serves are independent of each other then no matter how many times she was successful in the first 9 attempts, it will not affect the 10th attempt. However, in part (a), we have to be successful twice for the first 9 times, that is where makes the big difference.
