---
title: "Final Project Proposal"
author: "Vivian Kong"
date: "10/21/2016"
output: html_document
---

## 1. Research Question
Load the data from the website of "Fivethirtyeight". My research topic is European terrorism fatalities. I want to find that total fatalties from terroirism incidents in Europe since 1970 to 2014. There were so many terrorrism attacks happened recently. I want to find out if there is a pattern of the terrisom attacks from 1970 to 2014.
```{r}
library(tidyr)
library(dplyr)
require(knitr)
Terrorism_Country<- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/terrorism/eu_terrorism_fatalities_by_country.csv", stringsAsFactors = FALSE, check.names = FALSE, na.strings = c("", "NA"))
kable(head(Terrorism_Country))
```

## 2. Cases 
The raw data records all the terroirism fatalities of each country from 1970 to 2014.

```{r}
nrow(Terrorism_Country)
ncol(Terrorism_Country)
```

There are 45 rows (1970 - 2014) and 13 columns (13 countries of Europe).

## 3. Data collection
The data is collected behind the story "The Rise Of Religiously Inspired Terrorism In France".

## 4. Type of study
The data is prospective study. It records all the attack of terrorisms of Europe from 1970 to 2014. 

## 5. Data Source

The raw data can be found at [http://www.start.umd.edu/gtd/] and [https://github.com/fivethirtyeight/data/tree/master/terrorism].

## 6. Explanatory
Year(categorical), Number of death in different couries(numerical)

## 7. Relevant summary
Provide summary statistics relevant to the research question.

```{r}
tc <- data.frame(Terrorism_Country)
colnames(tc)[13] <- "UK"
tc1 <- within(tc, {Belgium <- as.numeric(as.character(Belgium))
Denmark <-as.numeric(as.character(Denmark))
France <-as.numeric(as.character(France))
Germany <-as.numeric(as.character(Germany))
Greece <-as.numeric(as.character(Greece))
Ireland <-as.numeric(as.character(Ireland))
Italy <-as.numeric(as.character(Italy))
Luxembourg <-as.numeric(as.character(Luxembourg))
Netherlands <-as.numeric(as.character(Netherlands))
Portugal <-as.numeric(as.character(Portugal))
Spain <-as.numeric(as.character(Spain))
UK<-as.numeric(as.character(UK))
})
tc1 %>% mutate(sum_year = rowSums(.[2:13]))
tc1 %>% summarise_each(funs(sum))
summary(tc1$UK)
summary(tc1$Spain)
summary(tc$France)
```











